### 2021-04-07 sections/2-methods.tex
notes
hierarchical extension of 2020 Berger et. al. paper

Write about methods \dots

>>>>

\subsection{Partition}
\label{subsec:methods:partition}

Partition algorithm for building the tree.
Lift this from the CHAODA paper.

Exact partition costing $\mathcal{O}(n^2)$ vs approximate partition using $\sqrt{n}$ seeds to achieve $\mathcal{O}(n)$ cost.

% latex does not seem to like math symbols in this heading
\subsection{\texorpdfstring{$\rho$}{p}-Nearest Neighbors Search}
\label{subsec:methods:rnn-search}

Modified binary search.
Lift this from CHESS paper.

\subsection{k-Nearest Neighbors Search}
\label{subsec:methods:knn-search}

Repeated $\rho$-NN search with where radius is modified with each iteration as guided by lfd of query ball.

Lift from CHESS paper as a starting point.

\subsection{Compression}
\label{subsec:methods:compression}

Encode and Decode algorithms.
These will be specific for each dataset and/or distance function.

% discrete vs continuous, and small alphabet vs large alphabet in discrete
